Title

### 2013-04-01 inc/model_results/rf_cav/rf_cav.tex
tweaks to the rf_cav model_results section, including a figure caption

The optimized RF cavity performance for the temporal compression of a pulse with the same initial photoemission conditions, but with $N = 10^{5}$ electrons, is shown in \ref{fig:rf_cav_num}\subref{fig:rf_cav_N1e5}.
In this case, intra-pulse space-charge effects act to further broaden the initial 100fs pulse duration to $\sim$6ps after the $\sim$1ns time-of-flight over the 10cm distance to the RF cavity.
The fact that almost the same RF field strength (495 kV/m) is required to generate a temporal focus at $z^{\prime} = $ 10cm is a direct consequence of the linear dependence of the longitudinal RF cavity force on $z$ (\ref{eq:RF_Force_z}), which means that the required restorative force is not dependent on $\sigma_{z}$ --- just as the focal length of a perfect optical lens is independent of its aperture size.
However, unlike in the dispersion limited case (\ref{fig:rf_cav_num}\subref{fig:rf_cav_N1}), the compressed pulse duration is now a factor of $\sim$4 less than the original 100fs laser pulse duration.
This additional pulse compression for the employed 1-to-1 image-to-object distance (magnification) ratio is made possible by the additional pulse bandwidth (and momentum chirp) generated by the space-charge effects --- in analogy to self-phase modulation (and dispersion) in fiber-grating laser pulse compression.\cite{strickland_compression_1985}
In this case, the $\sim$100-fold increase in the transverse pulse size (corresponding to a $10^{4}\times$ reduced peak pulse charge density) aids the temporal compression by greatly diminishing Coulomb effects that counteract the reduction in electron pulse duration.
Again, a stronger (and suitably phased) RF field will result in an even shorter compressed pulse duration as the distance to the temporal focus behind the RF cavity is reduced.

>>>>

The optimized RF cavity performance for the temporal compression of a pulse with the same initial photoemission conditions, but with $N = 10^{5}$ electrons, is shown in \ref{fig:rf_cav_num}\subref{fig:rf_cav_N1e5}.
In this case, intra-pulse space-charge effects act to further broaden the initial 100fs pulse duration to $\sim$6ps after the $\sim$1ns time-of-flight over the 10cm distance to the RF cavity.
The fact that almost the same RF field strength (495 kV/m) is required to generate a temporal focus at $z^{\prime} = $ 10cm is a direct consequence of the linear dependence of the longitudinal RF cavity force on $z$ (\ref{eq:RF_Force_z}), which means that the required restorative force is not dependent on $\sigma_{z}$ --- just as the focal length of a perfect optical lens is independent of its aperture size.
However, unlike in the dispersion limited case (\ref{fig:rf_cav_num}\subref{fig:rf_cav_N1}), the compressed pulse duration is now a factor of $\sim$2 less than the original 100fs laser pulse duration ($\sim 48$ fs).
This additional pulse compression for the employed 1-to-1 image-to-object distance (magnification) ratio is made possible by the additional pulse bandwidth (and momentum chirp) generated by the space-charge effects --- in analogy to self-phase modulation (and dispersion) in fiber-grating laser pulse compression.\cite{strickland_compression_1985}
In this case, the $\sim$20-fold increase in the transverse pulse size (corresponding to a $\sim400\times$ reduced peak pulse charge density) aids the temporal compression by greatly diminishing Coulomb effects that counteract the reduction in electron pulse duration.
Again, in analogy to optical imaging, a stronger (and suitably phased) RF field will result in an even shorter compressed pulse duration as the distance to the temporal focus behind the RF cavity is reduced.

### 2013-04-01 inc/model_results/rf_cav/rf_cav_plot.tex
tweaks to the rf_cav model_results section, including a figure caption

\begin{figure}
  \centerline {
    \subfloat[][]{
      \label{fig:rf_cav_N1}
      \begin{tikzpicture}
        \input{rf_cav_N1}
      \end{tikzpicture}
    }
    \subfloat[][]{
      \label{fig:rf_cav_N1e5}
      \begin{tikzpicture}
        \input{rf_cav_N1e5}
      \end{tikzpicture}
    }
  }
  \caption[Short]{
    Long
  }
  \label{fig:rf_cav_num}
\end{figure}

>>>>

\begin{figure}
  \centerline {
    \subfloat[][]{
      \label{fig:rf_cav_N1}
      \begin{tikzpicture}
        \input{rf_cav_N1}
      \end{tikzpicture}
    }
    \subfloat[][]{
      \label{fig:rf_cav_N1e5}
      \begin{tikzpicture}
        \input{rf_cav_N1e5}
      \end{tikzpicture}
    }
  }
  \caption[Dynamics of the pulse length and width under the influence of an RF cavity]{
    Dynamics of the pulse length (green) and width (red) under the influence of an RF cavity placed at $z' = 0$.
    The employed idealized pulses start at $z'= -100$ cm with velocity $v_{\smallzero} = \sim 84 \times 10^{6}$ m/s (20kV) and initial HW1/eM width of 100 $\mu$m and length $\sim 8.4 \mu$m ($v_{\smallzero} \cdot $ 100fs).
    \subref{fig:rf_cav_N1} has $N=1$ electron and demonstrates one-to-one imaging of the initial pulse length at the focus at $ z' = 100 $ cm.
    \subref{fig:rf_cav_N1e5} has $ N = 1 \times 10^5 $ electrons, whose added broadening allows for the factor of two reduction in pulse length at the focus ($\sim 48$ fs).
  }
  \label{fig:rf_cav_num}
\end{figure}
